Draft1

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Add map to draft

@@

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.

>>>>

In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.  To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.  This figure is included below.

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

# Drop unnecessary column 1
WayofTeaching$X <- NULL

# Change data from long to wide format
WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")

# Delete variable name in Year columns
names(WT) <- gsub("WayofTeaching.", "", names(WT))

# Duplicate df for future use
WT2 <- WT

# Generate a new column with mean of all other columns
WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010")), na.rm = TRUE)

# Drop year columns, leaving only mean column
WT$'2001' <- NULL
WT$'2002' <- NULL
WT$'2003' <- NULL
WT$'2004' <- NULL
WT$'2005' <- NULL
WT$'2006' <- NULL
WT$'2007' <- NULL
WT$'2008' <- NULL
WT$'2009' <- NULL
WT$'2010' <- NULL
WT$'2011' <- NULL
WT$'2012' <- NULL
WT$'2013' <- NULL
WT$row.names <- NULL

# Create 
WT[, 3] <- round(log(WT[, 3]), digits = 2)
```

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
library(googleVis)

# Plot
WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

@@

-------------------------

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.  This relationship can be seen in the following regression output table.
